### 2019-03-18 manuscript.tex
Working with chyun

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
\newcommand{\cf}[1]{\comment{CFS only: #1}}
\newcommand{\jdcmt}[1]{\comment{JD: #1}}
\newcommand{\mlcmt}[1]{\comment{MLi: #1}}

@@

It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cf{updated Sep 18}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.  Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}. \jdcmt{Not all UN sources are the same. The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

@@

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cf{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cf{\cite{Rima08}}*

@@

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}

@@

\cf{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

@@

--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% put religion into consideration of our findings (i.e., national distribution of religion, how many muslins in each country)
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}
% \cf{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
% Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}

@@

% Spatial Bayesian model \cite{KandNwak09}
% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
% a possibility of a multicultural egalitarian society \cite{Wade11}
% success in community education program to abandon FGC \cite{DiopAske09}
%\cf{convention theory mainly work on norms or also on behaviour change?  There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?  As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
% "I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms. In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed. The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.

\cf{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}

@@

%\cf{a sentence on the national FGC policy of the 4 nations and gender law}
% "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."

@@

%\cf{Bicchieri's norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cf{normative norm?}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cf{empirical norm?}?

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cf{I don't know if I want to cite \cite{EffeVogt15}.  It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).

% \cf{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
 * Festinger (1950?):  Social pressure in informal groups

>>>>

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
\newcommand{\cfonly}[1]{\comment{CFS only: #1}}
\newcommand{\jdcmt}[1]{\comment{JD: #1}}
\newcommand{\mlcmt}[1]{\comment{MLi: #1}}

@@

It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cfonly{updated Sep 18}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.  Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
academic.}\cfcmt{UN is supposed to be reliable and often quoted by academic papers}. \jdcmt{Not all UN sources are the same. The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)) \jd{How do you see the Tostan fitting in? Or is that a cfonly thing?.

@@

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cfonly{\cite{Rima08}}*

@@

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}

@@

\cfcmt{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

@@

--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cfcmt{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% put religion into consideration of our findings (i.e., national distribution of religion, how many muslins in each country)
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}
% \cfcmt{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
% Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}

@@

% Spatial Bayesian model \cite{KandNwak09}
% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
% a possibility of a multicultural egalitarian society \cite{Wade11}
% success in community education program to abandon FGC \cite{DiopAske09}
%\cfcmt{convention theory mainly work on norms or also on behaviour change?  There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?  As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
% "I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms. In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed. The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.

\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}

@@

%\cfcmt{a sentence on the national FGC policy of the 4 nations and gender law}
% "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."

@@

%\cfcmt{Bicchieri's norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cfcmt{normative norm?}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cfcmt{empirical norm?}?

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.  It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).

% \cfcmt{TOSTAN uses a strategy based on convention theory's critical mass to eradicate FGC (see (Wils13}}
 * Festinger (1950?):  Social pressure in informal groups
